---
title: "02_Using R did package"
author: "YC"
date: "2024-06-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Using the did package in R

Following the example vignette provided by the [did package user guide](https://bcallaway11.github.io/did/articles/did-basics.html) to explore the use of this package to conduct did analysis.

```{r}
library(did)
library(ggplot2)
```


### Example dataset

Simulate a dataset with 4 time periods with both treatment and control groups as following:

```{r}
# set seed
set.seed(1814)

# 4 time periods
time.periods = 4

# add dynamic effects
sp = reset.sim(time.periods, n=4000, ipw=F, reg=F)
sp$te.e = 1:time.periods

# generate data
dta = build_sim_dataset(sp)

# dat quick view
head(dta)

```
#### Plot the data

```{r}

ggplot(data=dta) +
  geom_jitter(aes(x=period+G/10, y=Y, color=as.factor(G)))+
  theme_bw()
  

```


### Estimating Group-Time Average Treatment Effects

```{r}
# estimate group-time average treatment effects using att_gt method
example_attgt = att_gt(yname = "Y",
                        tname = "period",
                        idname = "id",
                        gname = "G",
                        xformla = ~X,
                        data = dta
                        )

# summarize the results
summary(example_attgt)

```

### Plot the group-time average treatment effects

```{r}
# plot the results
ggdid(example_attgt)

```



### Aggregating group-time ATE

##### Simple Aggregation

```{r}
agg.simple <- aggte(example_attgt, type = "simple")
summary(agg.simple)
```
##### Dynamic effects and Event Studies

```{r}
agg.es <- aggte(example_attgt, type = "dynamic")
summary(agg.es)

```

```{r}
ggdid(agg.es)

```


##### Group specific effects

```{r}
agg.gs <- aggte(example_attgt, type = "group")
summary(agg.gs)
ggdid(agg.gs)
```

##### Calendar Time effects

```{r}
agg.ct <- aggte(example_attgt, type = "calendar")
summary(agg.ct)
ggdid(agg.ct)
```



